The Effect of Fictional Reappraisal on Subjective Ratings Toward Images

### 2025-11-11 paper/manuscript.qmd
minor

The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific\textcopyright, Sona (ref), social media platforms, university classrooms, and snowball sampling. This strategy yielded a heterogeneous pool of both incentivised and non-incentivised individuals, including students and members of the general population from England, France, Italy, Colombia, and Spain.

@@

The Consumption of Pornography Scale – General [COPS, @hatch2023consumption] is a 34-itemmeasure assessing pornography use across multiple dimensions, including frequency, duration and recency of sexual activity. Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day) and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes). An additional item assessed the recency of any sexual activity, with response options ranging from within the past 24 hours to more than a year ago.

@@

In the first phase, participants were told that the study aimed to validate a new image-generation algorithm. They were informed that they would see images allegedly produced by this algorithm intermixed with real photographs, each preceded by a cue indicating whether the upcoming image was of an “AI-generated” or “Photograph” origin. Their task was to rate each image on arousal, enticement, and valence.
Each participant viewed 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO, @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki]. Each trial followed a fixed timing sequence: a fixation cross (750 ms), a color-coded textual cue (1,250 ms), another fixation cross (500 ms), then the image (2,500 ms). Cues were presented in red, green, or blue, with colors randomly assigned across participants.

@@

In the final phase, participants viewed the same 60 images, presented in a new randomized order. Each was preceded by a 500 ms fixation cross and displayed for 1,000 ms. This time, participants rated each image on perceived realism—how photographic or lifelike it appeared.

>>>>

The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific\textcopyright, Sona Systems, social media platforms, university classrooms, and snowball sampling. This strategy yielded a heterogeneous pool of both incentivised and non-incentivised individuals, including students and members of the general population from England, France, Italy, Colombia, and Spain.

@@

The Consumption of Pornography Scale – General [COPS, @hatch2023consumption] is a 34-item measure assessing pornography use across multiple dimensions, including frequency, duration and recency of sexual activity. Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day) and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes). An additional item assessed the recency of any sexual activity, with response options ranging from within the past 24 hours to more than a year ago.

@@

In the first phase, participants were told that the study aimed to validate a new image-generation algorithm. They were informed that they would see images allegedly produced by this algorithm intermixed with real photographs, each preceded by a cue indicating whether the upcoming image was of an “AI-generated” or “Photograph” origin. Their task was to rate each image on arousal, enticement, and valence.
Each participant viewed, in a randomised order, 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO, @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki]. Each trial followed a fixed timing sequence: a fixation cross (750 ms), a color-coded textual cue (1,250 ms), another fixation cross (500 ms), then the image (2,500 ms). Cues were presented in red, green, or blue, with colors randomly assigned across participants.

@@

In the final phase, participants viewed the same 60 images, presented in a new randomised order. Each was preceded by a 500 ms fixation cross and displayed for 1,000 ms. This time, participants rated each image on perceived realism—how photographic or lifelike it appeared.
